### 2009-06-16 paper.tex
last edits
post-submission change to abstract

% figures in figs_plos:
% 1: parent.pdf
% 2: threeway.pdf
% 3: stree-with-structure.pdf
% 4: stree-mutations-with-structures.pdf
% 5: perfect.pdf
% 6: ama.pdf

@@

In our tests, incorporation of basepair structure was the most important factor for alignment accuracy;
appropriate use of posterior-decoding was the next most important factor;
and fine details of the model were least important.
Since posterior-decoding heuristics can be substantially faster than exact phylogenetic ML,
this motivates the use of sum-over-pairs (and approximate sum-over-pairs) heuristics
for paleogenetics and other alignment problems.

>>>>

% figures in figs_plos:
% 1: stree-with-structure.pdf
% 2: stree-mutations-with-structures.pdf
% 3: perfect.pdf
% 4: ama.pdf

@@

In our tests, incorporation of basepair structure was the most important factor for alignment accuracy;
appropriate use of posterior-decoding was the next most important factor;
and fine details of the model were least important.
Since posterior-decoding heuristics can be substantially faster than exact phylogenetic inference,
this motivates the use of sum-over-pairs (and approximate sum-over-pairs) heuristics where possible,
with transducer composition reserved for exact ML and MCMC inference on phylogenies.
We discuss possible ways to make these phylogenetic inferences tractable.
